### 2021-04-08 Main_Figures/Global_trait_spectrum.Rmd
Supp mat

  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4, xmax = -2.85,ymin = 2.05, ymax = 3.95)+
     annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -4.1, ymax = -3.25) +
    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.35,ymin = 0.8, ymax = 1.45) +
    annotation_raster(large_flower_1, xmin = 3.25, xmax = 4.25,ymin = 1.2, ymax = 2.45) +
    annotation_raster(flower_small_1, xmin = -3.60, xmax = -2.55,ymin = -2.2, ymax = -1.60) +
    annotation_raster(herb_1, xmin = 2.6, xmax = 3.1,ymin = -2.8, ymax = -2)

      #ADD LABELS
  rownames(PC$L) <- c("S", "FN", "FS", "SL", "ON", "PH" )

>>>>

  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
     annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -4.1, ymax = -3.25) +
    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)

      #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )
